Title: A proof-of-concept study

### 2022-01-25 paper.tex
update

  \begin{figure*}
    \subfigure[Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
               (photons s$^{-1}$ deg$^{-2}$) in the 0.6-1.0 keV range,\
               using a Hammer-Aitoff projection. Throughout this paper we show sky maps\
               in Galactic coordinates centered on the Galactic center and observed by the solar position.\
               The red arrow at the center of the\
               top panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
               to the disk normal in 1.2 Myr.]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xraymap.png}
      \label{fig__xray_0.8keV_angle_000}
     }
    \subfigure[Comparison of observed (black; \citealt{Predehl2020}) and simulated (red) one-dimensional\
               count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\
               cut at various galactic latitudes (as labelled).]
     {
      \includegraphics[width=\linewidth]{figures/fig__xray-profile-0.8keV-000.png}
      \label{fig__x-ray-profile-0.8keV-000}
     }
    \caption{}
    \label{fig_xray}
  \end{figure*}

>>>>

  \begin{figure*}
    \subfigure[Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
               (photons s$^{-1}$ deg$^{-2}$) in the 0.6-1.0 keV range,\
               using a Hammer-Aitoff projection. Throughout this paper we show sky maps\
               in Galactic coordinates centered on the Galactic center and observed by the solar position.\
               The red arrow at the center of the\
               top panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
               to the disk normal in 1.2 Myr.]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xraymap.png}
      \label{fig__xray_0.8keV_angle_000}
     }
    \subfigure[Comparison of simulated (red) and observed (black; \citealt{Predehl2020}) one-dimensional\
               count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\
               cut at various galactic latitudes (as labelled).]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xray-profile-0.8keV-000.png}
      \label{fig__x-ray-profile-0.8keV-000}
     }
    \caption{}
    \label{fig_xray}
  \end{figure*}
